---
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.path = "README_figs/README-")

library(betareg)
library(broom)
library(car)
library(DHARMa) # glmmTMB model diagnostics
library(emmeans)
library(ggplot2)
library(ggpubr)
library(glmmTMB) # Package for zero-inflated mixed-model
library(grid)
library(gridExtra)
library(emmeans)
library(knitr)
library(lme4) # Needed for R2 calculation
library(nlme)
library(MuMIn)
library(lmerTest)
library(lmtest)
library(tidyverse)

database.full   = read.csv("swipedataanglesallfull.csv") %>%
  mutate(UID      = paste(ID, Group))

#46 in full (47 actually, 1 is a dupe name)
read.csv("swipedataanglesallfull.csv") %>%
  select(ID) %>%
  pull() %>%
  unique() %>%
  length(.)

#30 in cleaned
read.csv("swipedataanglesall.csv") %>%
  select(ID) %>%
  pull() %>%
  unique() %>%
  length(.)

#30 in cleaned
database.screen.id = read.csv("swipedataanglesall.csv") %>%
  mutate(UID      = paste(ID, Group)) %>%
  select(UID) %>%
  pull() %>%
  unique()

database.full = database.full %>%
  mutate(Included = ifelse(UID %in% database.screen.id, TRUE, FALSE))

store = database.full %>%
  group_by(Included, UID) %>%
  slice(1) %>%
  summarise(
    Count = n()
  )

mControl = glmmTMBControl(
  optCtrl = list(
    iter.max = 1e6,
    eval.max = 1e6
  )
)

range      <- 180
binWidth   <- 11.25
binCounts  <- (range / binWidth) + 1 #16
ns         <- seq(0, binCounts - 1)
ns         <- ns * binWidth
ns.corr    <- ns - 90

diameterLen <- 100
textSize <- 4
plotMargins <- c(0,
                 0,
                 0,
                 0)

Round <- function(x,y) {
  if((y - x %% y) <= x %% y) { x + (y - x %% y)}
  else { x - (x %% y)}
}
```

## Examining Effects of Training Duration on Humans’ Resurgence and Variability Using a Novel Touchscreen Procedure

## Authors

- Carolyn M. Ritchey (Auburn University)

- Yuto Mizutani (Aichi Gakuin University)

- Toshikazu Kuroda (Huckle Co., Ltd., Aichi, Japan; Aichi Bunkyo University)

- Shawn Gilroy (Louisiana State University)

- Christopher A. Podlesnik (Auburn University)

## Abstract

Resurgence occurs when a previously reinforced and then extinguished target response increases due to reducing/eliminating an alternative source of reinforcement or punishing an alternative response. We evaluated whether duration of reinforcement history for a target response (1) affects the degree to which a resurgence effect is observed in humans and (2) produces different gradients of response generalization around target responding during extinction testing. We arranged a novel touchscreen interface in which university students could swipe a 3D soccer ball to spin any direction. In Phase 1, the first direction swiped became the target and produced points exchangeable for money for 3 or 1 min across two groups. The first swipe was recorded but had no programmed consequence in a third group. In Phase 2, swipes 180-degrees from the target resulted in points for 3 min in all groups. Point deliveries ceased for 2 min to test for resurgence in Phase 3. Target responses resurged during testing to a relatively greater extent with longer Phase-1 training but gradients of response generalization did not differ among groups. These findings extend prior research on the role of training duration on resurgence. We discuss methodological and conceptual issues surrounding the assessment of response generalization in resurgence. 

## Included files


Data:

- Swipe U Value.csv (Phase-level U values calculated for each individual/phase)

- RawDataOG_ALL.csv (Pre-binned and cleaned data with responding across individuals)

- swipedataanglesall.csv (Raw data regarding swipes from participants with clean data)

- swipedataanglesallfull.csv (Raw data regarding swipes from all participants)

## Study Results (with and without data cleaning)

### Descriptives (U-values)

```{r descriptiveScreened}

uData     <- read.csv("Swipe U Value.csv", header = TRUE)

uData.grp <- groupedData(Uvalue ~ as.factor(Group) * 
                           as.factor(Phase) * 
                           as.numeric(Time) | id, 
                         data = uData)

fullModel <- gls(Uvalue ~ Group * Phase * Time, 
                 data        = uData.grp,
                 method      = "ML",
                 correlation = corCompSymm(form = ~ 1 | id))

rstModl.1 <- gls(Uvalue ~ Group + Phase + Time + Group:Phase + Group:Time + Phase:Time, 
                 data        = uData.grp,
                 method      = "ML",
                 correlation = corCompSymm(form = ~ 1 | id))

anova(fullModel, rstModl.1)

rstModl.2 <- gls(Uvalue ~ Group + Phase + Time + Group:Phase + Phase:Time, 
                 data        = uData.grp,
                 method      = "ML",
                 correlation = corCompSymm(form = ~ 1 | id))

anova(rstModl.1, rstModl.2)

rstModl.3 <- gls(Uvalue ~ Group + Phase + Time + Group:Phase, 
                 data        = uData.grp,
                 method      = "ML",
                 correlation = corCompSymm(form = ~ 1 | id))

anova(rstModl.2, rstModl.3)

rstModl.4 <- gls(Uvalue ~ Group + Phase + Time, 
                 data        = uData.grp,
                 method      = "ML",
                 correlation = corCompSymm(form = ~ 1 | id))

anova(rstModl.3, rstModl.4)

summary(rstModl.2)

uData.grp$Phase = as.factor(uData.grp$Phase)
uData.grp$pred  = predict(rstModl.2)

ggplot(uData.grp, aes(Time, pred,
                      color = Phase)) +
  geom_line() +
  ylim(0, 1) +
  labs(
    y = "U Values",
    x = "Minute",
    title = "Screened dataset (Null Except for Intercept)"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~ Group)

```

### RQ1: To what degree does the duration of target-reinforcement history in Phase 1 influence observed rates of resurgence as target responses as a proportion of previously reinforced responses (i.e., Target, Alternative)?

#### Screened Set

```{r rq1screenedRE, message=FALSE, warning=FALSE}

colData <- read.csv("RawDataOG_ALL.csv", check.names = FALSE) %>%
  gather(Time, Frequency, -Group, -PID, -Tag) %>%
  mutate(Response = ifelse(str_detect(Time, "ALT_"), "Alternative", "Target"),
         Time = str_extract(Time, "\\-*\\d+\\.*\\d*"),
         Time = as.numeric(Time),
         Phase = "B",
         Phase = ifelse(Time < 10, "A", Phase),
         Phase = ifelse(Time > 18, "C", Phase),
         Time = as.numeric(Time) - 18) %>%
  spread(Response, Frequency) %>%
  mutate(TotalInBin = Target + Alternative,
         Proportion = Target / TotalInBin) %>%
  mutate(Group = factor(Group,
                        levels = c("No Baseline", "Short Baseline", "Long Baseline"),
                        labels = c("None", "Short", "Long"))) %>%
  filter(Group != "Baseline Only") %>%
  filter(Phase == "C") %>%
  filter(Proportion > 0 & Proportion < 1)

RE.NO <- betareg(Proportion ~ Time * Group,
                 data      = colData,
                 link      = "logit",
                 na.action = na.omit)

RE.1 <- glmmTMB(Proportion ~ Time * Group + (1 | PID),
                control   = mControl,
                family    = beta_family(),
                REML      = TRUE,
                na.action = na.omit,
                data      = colData)

RE.2 <- glmmTMB(Proportion ~ Time * Group + (Time | PID),
                control   = mControl,
                family    = beta_family(),
                REML      = TRUE,
                na.action = na.omit,
                data      = colData)

AICc(RE.NO, RE.1, RE.2) %>%
  kable(caption = "RE Comparisons (RE.NO Selected)") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

Model evaluations suggested that beta regression alone [RE.NO], without random effects, best characterized the available data.

```{r rq1screenedFE, message=FALSE, warning=FALSE}

FE.0 <- betareg(Proportion ~ Time * Group,
                 data = colData,
                 link = "logit",
                 na.action = na.omit)

FE.1 <- betareg(Proportion ~ Time + Group,
                data = colData,
                link = "logit",
                na.action = na.omit)

AICc(FE.0, FE.1) %>%
  kable(caption = "FE Comparisons (FE.1 Selected, no interaction)") %>%
  kableExtra::kable_styling(full_width = TRUE)
 
colData$pred = predict(FE.1,
                       level = 0,
                       type = "response",
                       re.form = NA)

colData$predi= predict(FE.1,
                       type = "response",
                       re.form = NULL)

pop = ggplot(colData, aes(Time, pred, color = Group)) +
  ylim(0,1) +
  theme_bw() +
  geom_line()

estimates = emmeans::emmeans(FE.1, ~ Time | Group, type = "response",
                             at = list(
                               Time = c(1, 2, 3, 4, 5, 6)
                               )
                             ) %>%
  as.data.frame()
 
ggplot(colData, aes(Time, predi,
                    color = Group,
                    group = PID)) +
  ylim(0,1) +
  theme_bw() +
  geom_line() +
  geom_ribbon(data = estimates, aes(y    = emmean,
                                    x    = Time,
                                    ymin = asymp.LCL,
                                    ymax = asymp.UCL),
              alpha = 0.5, inherit.aes = FALSE) +
  geom_line(data = estimates, aes(y    = emmean,
                                  x    = Time,),
            size = 2, inherit.aes = FALSE) +
  labs(
    y = "Proportion of Target",
    x = "10s Bin",
    title = "Screened dataset (Null Except for Intercept)"
  ) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Group)

summary(FE.1)

```

#### Unscreened Set

```{r rq1unscreenedRE, message=FALSE, warning=FALSE}

database <- database.full %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Responding = Angle.Diff,
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding >  270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding >  180, 180-abs(Responding), Responding)) %>%#,
  filter(Phase == "C") %>%
  mutate(Responding = abs(Responding)) %>%
  mutate(Response   = ifelse(Responding <= 22.5, "Target", "Other")) %>%
  mutate(Response   = ifelse(Responding >= 157.5, "Alternative", Response)) %>%
  mutate(Response   = ifelse(Response == "Other", "Control", Response)) %>%
  # Normalize sides
  mutate(Responding = ifelse(Responding > 90, Responding - 90, Responding)) %>%
  # Normalize to zero
  mutate(Responding = Responding - 45)

for (i in unique(database$UID)) {
  startTime <- database %>%
    filter(UID == i) %>%
    select(Time) %>%
    pull() %>%
    min()

  database[database$UID == i, "SessionTime"] <- (database[database$UID == i, 
                                                         "Time"] - startTime)/1000
  database[database$UID == i, "Time"] <- floor(database[database$UID == i, 
                                                       "SessionTime"] / 20) + 1
}

database.organized <- database %>%
  group_by(UID, Group, Time, Response) %>%
  summarise(
    Frequency = n()
  ) %>%
  spread(Response, Frequency) %>%
  mutate(Alternative = ifelse(is.na(Alternative), 0, Alternative),
         Control     = ifelse(is.na(Control),     0, Control),
         Target      = ifelse(is.na(Target),      0, Target)) %>%
  mutate(Proportion = Target / (Alternative + Target)) %>%
  filter(Proportion > 0 & Proportion < 1)

RE.NO <- betareg(Proportion ~ Time * Group,
                 data      = database.organized,
                 link      = "logit",
                 na.action = na.omit)

RE.1 <- glmmTMB(Proportion ~ Time * Group + (1 | UID),
                control   = mControl,
                family    = beta_family(),
                REML      = TRUE,
                na.action = na.omit,
                data      = database.organized)

RE.2 <- glmmTMB(Proportion ~ Time * Group + (Time | UID),
                control   = mControl,
                family    = beta_family(),
                REML      = TRUE,
                na.action = na.omit,
                data      = database.organized)

AICc(RE.NO, RE.1, RE.2) %>%
  kable(caption = "RE Comparisons (RE.1 Selected)") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

Model evaluations suggested that beta regression with random intercepts (ID) best characterized the data.

```{r rq1unscreenedFE, message=FALSE, warning=FALSE}

FE.0 <- glmmTMB(Proportion ~ Time * Group + (1 | UID),
                control   = mControl,
                family    = beta_family(),
                REML      = FALSE,
                na.action = na.omit,
                data      = database.organized)

FE.1 <- glmmTMB(Proportion ~ Time + Group + (1 | UID),
                control   = mControl,
                family    = beta_family(),
                REML      = FALSE,
                na.action = na.omit,
                data      = database.organized)

AICc(FE.0, FE.1) %>%
  kable(caption = "FE Comparisons (FE.1 Selected, no interaction)") %>%
  kableExtra::kable_styling(full_width = TRUE)

database.organized$pred = predict(FE.1,
                                  level = 0,
                                  type = "response",
                                  re.form = NA)

database.organized$predi = predict(FE.1,
                                   type = "response",
                                   re.form = NULL)

pop = ggplot(database.organized, aes(Time, pred, color = Group)) +
  ylim(0,1) +
  theme_bw() +
  geom_line()

estimates = emmeans(FE.1, ~ Time | Group, type = "response",
                    at = list(
                      Time = c(1, 2, 3, 4, 5, 6)
                      )) %>%
  as.data.frame()

database.organized = database.organized %>% 
  ungroup()

ggplot(database.organized, aes(Time, predi,
                               color = Group,
                               group = UID)) +
  ylim(0,1) +
  theme_bw() +
  geom_line() +
  geom_ribbon(data = estimates, aes(y    = response,
                                    x    = Time,
                                    ymin = lower.CL,
                                    ymax = upper.CL),
              alpha = 0.5,
              inherit.aes = FALSE) +
  geom_line(data = estimates, aes(y    = response,
                                  x    = Time), 
            size = 2,
            inherit.aes = FALSE) +
  labs(
    y = "Proportion of Target",
    x = "10s Bin",
    title = "Unscreened dataset (effect for Time)"
  ) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Group)

summary(FE.1)

```

### RQ2: Does the duration of target-reinforcement history in Phase 1 contribute to different gradients of non-reinforced/control responding around targeted responding when undergoing extinction of alternative responding? 

#### Screened Set

```{r rq3ScreenedHisto, message=FALSE}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Group = as.character(Group),
         Group = substr(Group, 7, nchar(Group))) %>%
  filter(Phase == "C" & Angle.Diff >= -90 & Angle.Diff <= 90) %>%
  mutate(Interval = cut(Angle.Diff, breaks = seq(-90, 90, length.out = 19))) %>%
  mutate(Interval = forcats::fct_explicit_na(Interval)) %>%
  filter(Interval != "(Missing)")

database$Group = factor(database$Group,
                        levels = c(
                          "Long",
                          "Short",
                          "None"
                        ))

linePlotData <- database %>%
  group_by(Group, Interval) %>%
  summarise(
    Counts = n()
  ) %>%
  mutate(
    xValue = rep(1:18)
  ) %>%
  ungroup() %>%
  mutate(Interval = str_replace(Interval, ']', ')'),
         Interval = as.factor(Interval))

xlabs <- levels(linePlotData$Interval)[levels(linePlotData$Interval) != "(Missing)"]

ggplot(linePlotData, aes(x = xValue, y = Counts,
                         fill = Group, group = Group,
                         pch = Group)) +
  geom_line() +
  geom_point(colour = "black", size = 4) +
  xlab("Distance from Original Swipe (Angle)") +
  ylab("Swipe Frequency") +
  papaja::theme_apa(base_size = 14) +
  scale_x_continuous(breaks = 1:18,
                     labels = xlabs) +
  geom_vline(xintercept = 7.75,  color = "black", linetype = "dashed", size = .75) +
  geom_vline(xintercept = 11.25, color = "black", linetype = "dashed", size = .75) +
  scale_fill_manual(name = "Group",
                     values = c("Long" = "#000000",
                                "Short" = "#666666",
                                "None" = "#FEFEFE")) +
  scale_shape_manual(
    values = c(
      "Long" = 21,
      "Short" = 22,
      "None" = 24
    )
  ) +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5,
                                   hjust = 1,
                                   color = "black"),
        legend.position = 'bottom')

```

```{r rq3ScreenedRose, message=FALSE, warning=FALSE, fig.width=8.5, fig.width=11}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Angle.Diff = ifelse(Angle.Diff < 0, Angle.Diff + 360, Angle.Diff),
         Response = NA) %>%
  filter(Phase != "A")

database <- database %>%
  group_by(ID, Phase) %>%
  mutate(MaxTime = max(Time)) %>%
  ungroup() %>%
  mutate(CurrentTime = MaxTime - Time) %>% # Adds in relative distance to end of phase
  filter(CurrentTime < 120000) # only pull last two min from included phases

d = database %>%
  mutate(Response = ifelse(Angle.Diff < 22.5,  "Target", Response),
         Response = ifelse(Angle.Diff > 337.5, "Target", Response),
         Response = ifelse(Angle.Diff < 202.5 & Angle.Diff > 157.5, "Alternative", Response),
         Response = ifelse(is.na(Response), "Control", Response),
         #Angle.Diff = plyr::round_any(Angle.Diff, 10, f = floor)) %>%
         Angle.Diff = Round(Angle.Diff, 22.5)) %>%
  group_by(Phase, Group, Angle.Diff, Response) %>%
  dplyr::summarise(
    Frequency = n()
  )

d$Group = factor(d$Group,
               levels = c("Group Long", "Group Short", "Group None"),
               labels = c("Long", "Short", "None"))

d$Phase = factor(d$Phase,
                 levels = c("B", "C"),
                 labels = c("Phase 2", "Phase 3"))

plotPrintAll <- ggplot(d, aes(x = Angle.Diff,
              y = Frequency,
              fill = Response)) +
  ggtitle("Swipe Directions across Both Phase 2 and Phase 3") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
      panel.grid   = element_blank(),
      axis.line    = element_line(color = "black",
                                  size = 0),
      panel.border = element_rect(size = 0),
      axis.ticks = element_line(size = 1),
      strip.background = element_blank(),
      #strip.text = element_blank(),
      panel.spacing = unit(1, "lines"),
      axis.text.y = element_blank(),
      axis.ticks.y.left = element_blank(),
      legend.position = "none") +
  facet_grid(Phase~Group)

d <- d %>% filter(Phase == "Phase 3")

plotPrintFocus <- ggplot(d, aes(x = Angle.Diff,
                                y = Frequency,
                                fill = Response)) +
  ggtitle("Swipe Directions across Phase 3 (Magnified)") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
        panel.grid   = element_blank(),
        axis.line    = element_line(color = "black",
                                    size = 0),
        panel.border = element_rect(size = 0),
        axis.ticks = element_line(size = 1),
        strip.background = element_blank(),
        panel.spacing = unit(1, "lines"),
        #strip.text = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = "bottom") +
  facet_grid(Phase~Group)

plotPrintAll

plotPrintFocus

```

```{r rq3ScreenedLevenes}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Responding = Angle.Diff) %>%
  filter(Phase == "C")

modDatabase.lev <- database %>%
  mutate(Responding = (Angle.Diff),
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding < -90,  180-abs(Responding), Responding),
         Responding = ifelse(Responding >  90,  180-abs(Responding), Responding),
         Group = factor(Group, levels=c("Group Long",
                                        "Group Short",
                                        "Group None")),
         Response = ifelse(Response == 1, "Target", "Alternative"),
         Response = ifelse(Responding > 22.5, "Control", Response),
         Response = ifelse(Responding < -22.5, "Control", Response)) %>%
  select(Group, Response, Responding) %>%
  filter(Response != "Control")

modDatabase.lev %>%
  group_by(Group) %>%
  dplyr::summarise(
    Ave = mean(Responding),
    sd  = sd(Responding)
  ) %>%
  kable(caption = "Reference Swipe (Screened)") %>%
  kableExtra::kable_styling(full_width = TRUE)

car::leveneTest(Responding ~ Group, data = modDatabase.lev) %>%
  tidy() %>% 
  kable(caption = "Levenes Test (Screened)") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

#### Unscreened Set

```{r rq3UnscreenedHisto, message=FALSE}

database <- database.full %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Group = as.character(Group),
         Group = substr(Group, 7, nchar(Group))) %>%
  filter(Phase == "C" & Angle.Diff >= -90 & Angle.Diff <= 90) %>%
  mutate(Interval = cut(Angle.Diff, breaks = seq(-90, 90, length.out = 19))) %>%
  mutate(Interval = forcats::fct_explicit_na(Interval)) %>%
  filter(Interval != "(Missing)")

database$Group = factor(database$Group,
                        levels = c(
                          "Long",
                          "Short",
                          "None"
                        ))

linePlotData <- database %>%
  group_by(Group, Interval) %>%
  summarise(
    Counts = n()
  ) %>%
  mutate(
    xValue = rep(1:18)
  ) %>%
  ungroup() %>%
  mutate(Interval = str_replace(Interval, ']', ')'),
         Interval = as.factor(Interval))

xlabs <- levels(linePlotData$Interval)[levels(linePlotData$Interval) != "(Missing)"]

ggplot(linePlotData, aes(x = xValue, y = Counts,
                         fill = Group, group = Group,
                         pch = Group)) +
  geom_line() +
  geom_point(colour = "black", size = 4) +
  xlab("Distance from Original Swipe (Angle)") +
  ylab("Swipe Frequency") +
  papaja::theme_apa(base_size = 14) +
  scale_x_continuous(breaks = 1:18,
                     labels = xlabs) +
  geom_vline(xintercept = 7.75,  color = "black", linetype = "dashed", size = .75) +
  geom_vline(xintercept = 11.25, color = "black", linetype = "dashed", size = .75) +
  scale_fill_manual(name = "Group",
                     values = c("Long" = "#000000",
                                "Short" = "#666666",
                                "None" = "#FEFEFE")) +
  scale_shape_manual(
    values = c(
      "Long" = 21,
      "Short" = 22,
      "None" = 24
    )
  ) +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5,
                                   hjust = 1,
                                   color = "black"),
        legend.position = 'bottom')

```

```{r rq3UnscreenedRose, message=FALSE, warning=FALSE, fig.width=8.5, fig.width=11}

database <- database.full %>%
  mutate(Angle.Diff = ifelse(Angle.Diff < 0, Angle.Diff + 360, Angle.Diff),
         Response = NA) %>%
  filter(Phase != "A")

database <- database %>%
  group_by(ID, Phase) %>%
  mutate(MaxTime = max(Time)) %>%
  ungroup() %>%
  mutate(CurrentTime = MaxTime - Time) %>% # Adds in relative distance to end of phase
  filter(CurrentTime < 120000) # only pull last two min from included phases

d = database %>%
  mutate(Response = ifelse(Angle.Diff < 22.5,  "Target", Response),
         Response = ifelse(Angle.Diff > 337.5, "Target", Response),
         Response = ifelse(Angle.Diff < 202.5 & Angle.Diff > 157.5, "Alternative", Response),
         Response = ifelse(is.na(Response), "Control", Response),
         #Angle.Diff = plyr::round_any(Angle.Diff, 10, f = floor)) %>%
         Angle.Diff = Round(Angle.Diff, 22.5)) %>%
  group_by(Phase, Group, Angle.Diff, Response) %>%
  dplyr::summarise(
    Frequency = n()
  )

d$Group = factor(d$Group,
               levels = c("Group Long", "Group Short", "Group None"),
               labels = c("Long", "Short", "None"))

d$Phase = factor(d$Phase,
                 levels = c("B", "C"),
                 labels = c("Phase 2", "Phase 3"))

plotPrintAll <- ggplot(d, aes(x = Angle.Diff,
              y = Frequency,
              fill = Response)) +
  ggtitle("Swipe Directions across Both Phase 2 and Phase 3") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
      panel.grid   = element_blank(),
      axis.line    = element_line(color = "black",
                                  size = 0),
      panel.border = element_rect(size = 0),
      axis.ticks = element_line(size = 1),
      strip.background = element_blank(),
      #strip.text = element_blank(),
      panel.spacing = unit(1, "lines"),
      axis.text.y = element_blank(),
      axis.ticks.y.left = element_blank(),
      legend.position = "none") +
  facet_grid(Phase~Group)

d <- d %>% filter(Phase == "Phase 3")

plotPrintFocus <- ggplot(d, aes(x = Angle.Diff,
                                y = Frequency,
                                fill = Response)) +
  ggtitle("Swipe Directions across Phase 3 (Magnified)") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
        panel.grid   = element_blank(),
        axis.line    = element_line(color = "black",
                                    size = 0),
        panel.border = element_rect(size = 0),
        axis.ticks = element_line(size = 1),
        strip.background = element_blank(),
        panel.spacing = unit(1, "lines"),
        #strip.text = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = "bottom") +
  facet_grid(Phase~Group)

plotPrintAll

plotPrintFocus

```

```{r rq3UnscreenedLevenes}

database <- database.full %>%
  mutate(Responding = Angle.Diff) %>%
  filter(Phase == "C")

modDatabase.lev <- database %>%
  mutate(Responding = (Angle.Diff),
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding < -90,  180-abs(Responding), Responding),
         Responding = ifelse(Responding >  90,  180-abs(Responding), Responding),
         Group = factor(Group, levels=c("Group Long",
                                        "Group Short",
                                        "Group None")),
         Response = ifelse(Response == 1, "Target", "Alternative"),
         Response = ifelse(Responding > 22.5, "Control", Response),
         Response = ifelse(Responding < -22.5, "Control", Response)) %>%
  select(Group, Response, Responding) %>%
  filter(Response != "Control")

modDatabase.lev %>%
  group_by(Group) %>%
  dplyr::summarise(
    Ave = mean(Responding),
    sd  = sd(Responding)
  ) %>%
  kable(caption = "Reference Swipe (Unscreened)") %>%
  kableExtra::kable_styling(full_width = TRUE)

car::leveneTest(Responding ~ Group, data = modDatabase.lev) %>%
  tidy() %>% 
  kable(caption = "Levenes Test (Unscreened)", "html") %>%
  kableExtra::kable_styling(full_width = TRUE,
                            position = "center")

```

