---
title: "Resurgence Touchscreen App"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(betareg)
library(broom)
library(car)
library(DHARMa) # glmmTMB model diagnostics
library(emmeans)
library(ggplot2)
library(ggpubr)
library(glmmTMB) # Package for zero-inflated mixed-model
library(grid)
library(gridExtra)
library(emmeans)
library(knitr)
library(lme4) # Needed for R2 calculation
library(MuMIn)
library(lmerTest)
library(lmtest)
library(tidyverse)

database.full   = read.csv("swipedataanglesallfull.csv") %>%
  mutate(UID      = paste(ID, Group))

#46 in full (47 actually, 1 is a dupe name)
read.csv("swipedataanglesallfull.csv") %>%
  select(ID) %>%
  pull() %>%
  unique() %>%
  length(.)

#30 in cleaned
read.csv("swipedataanglesall.csv") %>%
  select(ID) %>%
  pull() %>%
  unique() %>%
  length(.)

#30 in cleaned
database.screen.id = read.csv("swipedataanglesall.csv") %>%
  mutate(UID      = paste(ID, Group)) %>%
  select(UID) %>%
  pull() %>%
  unique()

database.full = database.full %>%
  mutate(Included = ifelse(UID %in% database.screen.id, TRUE, FALSE))

store =
database.full %>%
  group_by(Included, UID) %>%
  slice(1) %>%
  summarise(
    Count = n()
  )

mControl = glmmTMBControl(
  optCtrl = list(
    iter.max = 1e6,
    eval.max = 1e6
  )
)

range      <- 180
binWidth   <- 11.25
binCounts  <- (range / binWidth) + 1 #16
ns         <- seq(0, binCounts - 1)
ns         <- ns * binWidth
ns.corr    <- ns - 90

diameterLen <- 100
textSize <- 4
plotMargins <- c(0,
                 0,
                 0,
                 0)

Round <- function(x,y) {
  if((y - x %% y) <= x %% y) { x + (y - x %% y)}
  else { x - (x %% y)}
}
```

### RQ1: To what degree does the duration of target-reinforcement history in Phase 1 influence observed rates of resurgence as target responses as a proportion of previously reinforced responses (i.e., Target, Alternative)?

#### Screened Set

```{r rq1screenedRE, message=FALSE, warning=FALSE}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Responding = Angle.Diff,
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding >  270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding >  180, 180-abs(Responding), Responding)) %>%#,
  filter(Phase == "C") %>%
  mutate(Responding = abs(Responding)) %>%
  mutate(Response   = ifelse(Responding <= 22.5,  "Target", "Other")) %>%
  mutate(Response   = ifelse(Responding >= 157.5, "Alternative", Response)) %>%
  mutate(Response   = ifelse(Response == "Other", "Control", Response)) %>%
  mutate(Responding = ifelse(Responding > 90,     Responding - 90, Responding)) %>%
  mutate(Responding = Responding - 45)

for (i in unique(database$UID)) {
  startTime <- database %>%
    filter(UID == i) %>%
    select(Time) %>%
    pull() %>%
    min()

  database[database$UID == i, "SessionTime"] <- (database[database$UID == i, 
                                                         "Time"] - startTime)/1000
  database[database$UID == i, "Time"] <- floor(database[database$UID == i, 
                                                       "SessionTime"] / 20) + 1
}

database.organized <- database %>%
  group_by(UID, Group, Time, Response) %>%
  summarise(
    Frequency = n()
  ) %>%
  spread(Response, Frequency) %>%
  mutate(Alternative = ifelse(is.na(Alternative), 0, Alternative),
         Control     = ifelse(is.na(Control),     0, Control),
         Target      = ifelse(is.na(Target),      0, Target)) %>%
  mutate(Proportion = Target / (Alternative + Target)) %>%
  filter(Proportion > 0 & Proportion < 1)

RE.NO <- betareg(Proportion ~ Time * Group,
                 data = database.organized,
                 link = "logit",
                 na.action = na.omit)

RE.1 <- glmmTMB(Proportion ~ Time * Group + (1 | UID),
                control = mControl,
                family=beta_family(),
                REML = TRUE,
                na.action = na.omit,
                data = database.organized)

RE.2 <- glmmTMB(Proportion ~ Time * Group + (Time | UID),
                control = mControl,
                family=beta_family(),
                REML = TRUE,
                na.action = na.omit,
                data = database.organized)

AICc(RE.NO, RE.1, RE.2) %>%
  kable(caption = "RE Comparisons [RE.NO Selected]") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

Model evaluations suggested that beta regression alone [RE.NO], without random effects, best characterized the available data.

```{r rq1screenedFE, message=FALSE, warning=FALSE}

FE.0 <- betareg(Proportion ~ Time * Group,
                 data = database.organized,
                 link = "logit",
                 na.action = na.omit)

FE.1 <- betareg(Proportion ~ Time + Group,
                data = database.organized,
                link = "logit",
                na.action = na.omit)

AIC(FE.0, FE.1) %>%
  kable(caption = "FE Comparisons [FE.1 Selected, no interaction]") %>%
  kableExtra::kable_styling(full_width = TRUE)
 
database.organized$pred = predict(FE.1,
                                  level = 0,
                                  type = "response",
                                  re.form = NA)

database.organized$predi= predict(FE.1,
                                 type = "response",
                                 re.form = NULL)

pop = ggplot(database.organized, aes(Time, pred, color = Group)) +
  ylim(0,1) +
  theme_bw() +
  geom_line()

estimates = emmeans::emmeans(FE.1, ~ Time | Group, type = "response",
                             at = list(
                               Time = c(1, 2, 3, 4, 5, 6)
                               )) %>%
  as.data.frame()
 
ggplot(database.organized, aes(Time, predi,
                                     color = Group,
                                     group = UID)) +
  ylim(0,1) +
  theme_bw() +
  geom_line() +
  geom_ribbon(data = estimates, aes(y    = emmean,
                                    x    = Time,
                                    ymin = asymp.LCL,
                                    ymax = asymp.UCL),
              alpha = 0.5, inherit.aes = FALSE) +
  geom_line(data = estimates, aes(y    = emmean,
                                  x    = Time,),
            size = 2, inherit.aes = FALSE) +
  labs(
    y = "Proportion of Target",
    x = "10s Bin",
    title = "Screened dataset (Null Except for Intercept)"
  ) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Group)

summary(FE.1)

```

#### Unscreened Set

Note: The AICc was close, but I prefer to go maximal (more complex) whenever possible.

```{r rq1unscreenedRE, message=FALSE, warning=FALSE}

database <- database.full %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Responding = Angle.Diff,
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding >  270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding >  180, 180-abs(Responding), Responding)) %>%#,
  filter(Phase == "C") %>%
  mutate(Responding = abs(Responding)) %>%
  mutate(Response   = ifelse(Responding <= 22.5, "Target", "Other")) %>%
  mutate(Response   = ifelse(Responding >= 157.5, "Alternative", Response)) %>%
  mutate(Response   = ifelse(Response == "Other", "Control", Response)) %>%
  # Normalize sides
  mutate(Responding = ifelse(Responding > 90, Responding - 90, Responding)) %>%
  # Normalize to zero
  mutate(Responding = Responding - 45)

for (i in unique(database$UID)) {
  startTime <- database %>%
    filter(UID == i) %>%
    select(Time) %>%
    pull() %>%
    min()

  database[database$UID == i, "SessionTime"] <- (database[database$UID == i, 
                                                         "Time"] - startTime)/1000
  database[database$UID == i, "Time"] <- floor(database[database$UID == i, 
                                                       "SessionTime"] / 20) + 1
}

database.organized <- database %>%
  group_by(UID, Group, Time, Response) %>%
  summarise(
    Frequency = n()
  ) %>%
  spread(Response, Frequency) %>%
  mutate(Alternative = ifelse(is.na(Alternative), 0, Alternative),
         Control     = ifelse(is.na(Control),     0, Control),
         Target      = ifelse(is.na(Target),      0, Target)) %>%
  mutate(Proportion = Target / (Alternative + Target)) %>%
  filter(Proportion > 0 & Proportion < 1)

RE.NO <- betareg(Proportion ~ Time * Group,
                 data = database.organized,
                 link = "logit",
                 na.action = na.omit)

RE.1 <- glmmTMB(Proportion ~ Time * Group + (1 | UID),
                control = mControl,
                family=beta_family(),
                REML = TRUE,
                na.action = na.omit,
                data = database.organized)

RE.2 <- glmmTMB(Proportion ~ Time * Group + (Time | UID),
                control = mControl,
                family=beta_family(),
                REML = TRUE,
                na.action = na.omit,
                data = database.organized)

AICc(RE.NO, RE.1, RE.2) %>%
  kable(caption = "RE Comparisons [RE.1 Selected]") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

```{r rq1unscreenedFE, message=FALSE, warning=FALSE}

FE.0 <- glmmTMB(Proportion ~ Time * Group + (1 | UID),
                control = mControl,
                family=beta_family(),
                REML = TRUE,
                na.action = na.omit,
                data = database.organized)

FE.1 <- glmmTMB(Proportion ~ Time + Group + (1 | UID),
                control = mControl,
                family=beta_family(),
                REML = TRUE,
                na.action = na.omit,
                data = database.organized)

AICc(FE.0, FE.1) %>%
  kable(caption = "FE Comparisons [FE.1 Selected, no interaction]") %>%
  kableExtra::kable_styling(full_width = TRUE)

database.organized$pred = predict(FE.1,
                                  level = 0,
                                  type = "response",
                                  re.form = NA)

database.organized$predi= predict(FE.1,
                                  type = "response",
                                  re.form = NULL)

pop = ggplot(database.organized, aes(Time, pred, color = Group)) +
  ylim(0,1) +
  theme_bw() +
  geom_line()

estimates = emmeans(FE.1, ~ Time | Group, type = "response",
                    at = list(
                      Time = c(1, 2, 3, 4, 5, 6)
                      )) %>%
  as.data.frame()

database.organized = database.organized %>% 
  ungroup()

ggplot(database.organized, aes(Time, predi,
                                     color = Group,
                                     group = UID)) +
  ylim(0,1) +
  theme_bw() +
  geom_line() +
  geom_ribbon(data = estimates, aes(y    = response,
                                    x    = Time,
                                    ymin = lower.CL,
                                    ymax = upper.CL),
              alpha = 0.5,
              inherit.aes = FALSE) +
  geom_line(data = estimates, aes(y    = response,
                                  x    = Time), 
            size = 2,
            inherit.aes = FALSE) +
  labs(
    y = "Proportion of Target",
    x = "10s Bin",
    title = "Unscreened dataset (effect for Time)"
  ) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Group)

summary(FE.1)

```

### RQ2: Does the duration of target-reinforcement history in Phase 1 contribute to different gradients of non-reinforced/control responding around targeted responding when undergoing extinction of alternative responding? 

#### Screened Set

```{r rq3ScreenedHisto, message=FALSE}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Group = as.character(Group),
         Group = substr(Group, 7, nchar(Group))) %>%
  filter(Phase == "C" & Angle.Diff >= -90 & Angle.Diff <= 90) %>%
  mutate(Interval = cut(Angle.Diff, breaks = seq(-90, 90, length.out = 19))) %>%
  mutate(Interval = forcats::fct_explicit_na(Interval)) %>%
  filter(Interval != "(Missing)")

database$Group = factor(database$Group,
                        levels = c(
                          "Long",
                          "Short",
                          "None"
                        ))

linePlotData <- database %>%
  group_by(Group, Interval) %>%
  summarise(
    Counts = n()
  ) %>%
  mutate(
    xValue = rep(1:18)
  ) %>%
  ungroup() %>%
  mutate(Interval = str_replace(Interval, ']', ')'),
         Interval = as.factor(Interval))

xlabs <- levels(linePlotData$Interval)[levels(linePlotData$Interval) != "(Missing)"]

ggplot(linePlotData, aes(x = xValue, y = Counts,
                         fill = Group, group = Group,
                         pch = Group)) +
  geom_line() +
  geom_point(colour = "black", size = 4) +
  xlab("Distance from Original Swipe (Angle)") +
  ylab("Swipe Frequency") +
  papaja::theme_apa(base_size = 14) +
  scale_x_continuous(breaks = 1:18,
                     labels = xlabs) +
  geom_vline(xintercept = 7.75, color="black", linetype="dashed", size=.75) +
  geom_vline(xintercept = 11.25, color="black", linetype="dashed", size=.75) +
  scale_fill_manual(name = "Group",
                     values = c("Long" = "#000000",
                                "Short" = "#666666",
                                "None" = "#FEFEFE")) +
  scale_shape_manual(
    values = c(
      "Long" = 21,
      "Short" = 22,
      "None" = 24
    )
  ) +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5,
                                   hjust=1,
                                   color = "black"),
        legend.position = 'bottom')

```

```{r rq3ScreenedRose, message=FALSE, warning=FALSE, fig.width=8.5, fig.width=11}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Angle.Diff = ifelse(Angle.Diff < 0, Angle.Diff + 360, Angle.Diff),
         Response = NA) %>%
  filter(Phase != "A")

database <- database %>%
  group_by(ID, Phase) %>%
  mutate(MaxTime = max(Time)) %>%
  ungroup() %>%
  mutate(CurrentTime = MaxTime - Time) %>% # Adds in relative distance to end of phase
  filter(CurrentTime < 120000) # only pull last two min from included phases

d = database %>%
  mutate(Response = ifelse(Angle.Diff < 22.5,  "Target", Response),
         Response = ifelse(Angle.Diff > 337.5, "Target", Response),
         Response = ifelse(Angle.Diff < 202.5 & Angle.Diff > 157.5, "Alternative", Response),
         Response = ifelse(is.na(Response), "Control", Response),
         #Angle.Diff = plyr::round_any(Angle.Diff, 10, f = floor)) %>%
         Angle.Diff = Round(Angle.Diff, 22.5)) %>%
  group_by(Phase, Group, Angle.Diff, Response) %>%
  dplyr::summarise(
    Frequency = n()
  )

d$Group = factor(d$Group,
               levels = c("Group Long", "Group Short", "Group None"),
               labels = c("Long", "Short", "None"))

d$Phase = factor(d$Phase,
                 levels = c("B", "C"),
                 labels = c("Phase 2", "Phase 3"))

plotPrintAll <- ggplot(d, aes(x = Angle.Diff,
              y = Frequency,
              fill = Response)) +
  ggtitle("Swipe Directions across Both Phase 2 and Phase 3") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
      panel.grid   = element_blank(),
      axis.line    = element_line(color = "black",
                                  size = 0),
      panel.border = element_rect(size = 0),
      axis.ticks = element_line(size = 1),
      strip.background = element_blank(),
      #strip.text = element_blank(),
      panel.spacing = unit(1, "lines"),
      axis.text.y = element_blank(),
      axis.ticks.y.left = element_blank(),
      legend.position = "none") +
  facet_grid(Phase~Group)

# plotPrintAll

d <- d %>%
  filter(Phase == "Phase 3")

plotPrintFocus <- ggplot(d, aes(x = Angle.Diff,
                           y = Frequency,
                           fill = Response)) +
  ggtitle("Swipe Directions across Phase 3 (Magnified)") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
        panel.grid   = element_blank(),
        axis.line    = element_line(color = "black",
                                    size = 0),
        panel.border = element_rect(size = 0),
        axis.ticks = element_line(size = 1),
        strip.background = element_blank(),
        panel.spacing = unit(1, "lines"),
        #strip.text = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = "bottom") +
  facet_grid(Phase~Group)

# plotPrint <- grid.arrange(plotPrintAll, plotPrintFocus,
#              heights=c(0.6, 0.4),
#              nrow = 2)

# plotPrint <- grid.arrange(plotPrintAll, plotPrintFocus,
#              heights=c(0.6, 0.4),
#              nrow = 2)

plotPrintAll

plotPrintFocus

#ggsave("Rose - Screened.png", plot = plotPrint, width = 8.5, height = 11, units = "in", dpi = 600)

```

```{r rq3ScreenedLevenes}

database <- database.full %>%
  filter(Included == TRUE) %>%
  mutate(Responding = Angle.Diff) %>%
  filter(Phase == "C")

modDatabase.lev <- database %>%
  mutate(Responding = (Angle.Diff),
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding < -90,  180-abs(Responding), Responding),
         Responding = ifelse(Responding >  90,  180-abs(Responding), Responding),
         Group = factor(Group, levels=c("Group Long",
                                        "Group Short",
                                        "Group None")),
         Response = ifelse(Response == 1, "Target", "Alternative"),
         Response = ifelse(Responding > 22.5, "Control", Response),
         Response = ifelse(Responding < -22.5, "Control", Response)) %>%
  select(Group, Response, Responding) %>%
  filter(Response != "Control")

modDatabase.lev %>%
  group_by(Group) %>%
  dplyr::summarise(
    Ave = mean(Responding),
    sd  = sd(Responding)
  ) %>%
  kable(caption = "Reference Swipe [Screened]") %>%
  kableExtra::kable_styling(full_width = TRUE)

car::leveneTest(Responding ~ Group, data = modDatabase.lev) %>%
  tidy() %>% 
  kable(caption = "Levenes Test [Screened]") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

#### Unscreened Set

```{r rq3UnscreenedHisto, message=FALSE}

database <- database.full %>%
  mutate(Angle.Diff = Angle - Base.Angle,
         Group = as.character(Group),
         Group = substr(Group, 7, nchar(Group))) %>%
  filter(Phase == "C" & Angle.Diff >= -90 & Angle.Diff <= 90) %>%
  mutate(Interval = cut(Angle.Diff, breaks = seq(-90, 90, length.out = 19))) %>%
  mutate(Interval = forcats::fct_explicit_na(Interval)) %>%
  filter(Interval != "(Missing)")

database$Group = factor(database$Group,
                        levels = c(
                          "Long",
                          "Short",
                          "None"
                        ))

linePlotData <- database %>%
  group_by(Group, Interval) %>%
  summarise(
    Counts = n()
  ) %>%
  mutate(
    xValue = rep(1:18)
  ) %>%
  ungroup() %>%
  mutate(Interval = str_replace(Interval, ']', ')'),
         Interval = as.factor(Interval))

xlabs <- levels(linePlotData$Interval)[levels(linePlotData$Interval) != "(Missing)"]

ggplot(linePlotData, aes(x = xValue, y = Counts,
                         fill = Group, group = Group,
                         pch = Group)) +
  geom_line() +
  geom_point(colour = "black", size = 4) +
  xlab("Distance from Original Swipe (Angle)") +
  ylab("Swipe Frequency") +
  papaja::theme_apa(base_size = 14) +
  scale_x_continuous(breaks = 1:18,
                     labels = xlabs) +
  geom_vline(xintercept = 7.75, color="black", linetype="dashed", size=.75) +
  geom_vline(xintercept = 11.25, color="black", linetype="dashed", size=.75) +
  scale_fill_manual(name = "Group",
                     values = c("Long" = "#000000",
                                "Short" = "#666666",
                                "None" = "#FEFEFE")) +
  scale_shape_manual(
    values = c(
      "Long" = 21,
      "Short" = 22,
      "None" = 24
    )
  ) +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5,
                                   hjust=1,
                                   color = "black"),
        legend.position = 'bottom')

```

```{r rq3UnscreenedRose, message=FALSE, warning=FALSE, fig.width=8.5, fig.width=11}

database <- database.full %>%
  mutate(Angle.Diff = ifelse(Angle.Diff < 0, Angle.Diff + 360, Angle.Diff),
         Response = NA) %>%
  filter(Phase != "A")

database <- database %>%
  group_by(ID, Phase) %>%
  mutate(MaxTime = max(Time)) %>%
  ungroup() %>%
  mutate(CurrentTime = MaxTime - Time) %>% # Adds in relative distance to end of phase
  filter(CurrentTime < 120000) # only pull last two min from included phases

d = database %>%
  mutate(Response = ifelse(Angle.Diff < 22.5,  "Target", Response),
         Response = ifelse(Angle.Diff > 337.5, "Target", Response),
         Response = ifelse(Angle.Diff < 202.5 & Angle.Diff > 157.5, "Alternative", Response),
         Response = ifelse(is.na(Response), "Control", Response),
         #Angle.Diff = plyr::round_any(Angle.Diff, 10, f = floor)) %>%
         Angle.Diff = Round(Angle.Diff, 22.5)) %>%
  group_by(Phase, Group, Angle.Diff, Response) %>%
  dplyr::summarise(
    Frequency = n()
  )

d$Group = factor(d$Group,
               levels = c("Group Long", "Group Short", "Group None"),
               labels = c("Long", "Short", "None"))

d$Phase = factor(d$Phase,
                 levels = c("B", "C"),
                 labels = c("Phase 2", "Phase 3"))

plotPrintAll <- ggplot(d, aes(x = Angle.Diff,
              y = Frequency,
              fill = Response)) +
  ggtitle("Swipe Directions across Both Phase 2 and Phase 3") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
      panel.grid   = element_blank(),
      axis.line    = element_line(color = "black",
                                  size = 0),
      panel.border = element_rect(size = 0),
      axis.ticks = element_line(size = 1),
      strip.background = element_blank(),
      #strip.text = element_blank(),
      panel.spacing = unit(1, "lines"),
      axis.text.y = element_blank(),
      axis.ticks.y.left = element_blank(),
      legend.position = "none") +
  facet_grid(Phase~Group)

# plotPrintAll

d <- d %>%
  filter(Phase == "Phase 3")

plotPrintFocus <- ggplot(d, aes(x = Angle.Diff,
                           y = Frequency,
                           fill = Response)) +
  ggtitle("Swipe Directions across Phase 3 (Magnified)") +
  coord_polar(theta = "x",
              start = 0) +
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = seq(0, 360, 22.5)) +
  xlab("") +
  ylab("") +
  scale_fill_manual(name = "Response",
                    values = c(Control = "#C6C5C3",
                               Alternative = "#8E8B8A",
                               Target = "black")) +
  jtools::theme_apa() +
  theme(axis.text    = element_text(color = "black"),
        panel.grid   = element_blank(),
        axis.line    = element_line(color = "black",
                                    size = 0),
        panel.border = element_rect(size = 0),
        axis.ticks = element_line(size = 1),
        strip.background = element_blank(),
        panel.spacing = unit(1, "lines"),
        #strip.text = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = "bottom") +
  facet_grid(Phase~Group)

# plotPrint <- grid.arrange(plotPrintAll, plotPrintFocus,
#              heights=c(0.6, 0.4),
#              nrow = 2)

plotPrintAll

plotPrintFocus

#ggsave("Rose - Screened.png", plot = plotPrint, width = 8.5, height = 11, units = "in", dpi = 600)

```

```{r rq3UnscreenedLevenes}

database <- database.full %>%
  mutate(Responding = Angle.Diff) %>%
  filter(Phase == "C")

modDatabase.lev <- database %>%
  mutate(Responding = (Angle.Diff),
         Responding = ifelse(Responding < -270, 360-abs(Responding), Responding),
         Responding = ifelse(Responding < -180, 180-abs(Responding), Responding),
         Responding = ifelse(Responding < -90,  180-abs(Responding), Responding),
         Responding = ifelse(Responding >  90,  180-abs(Responding), Responding),
         Group = factor(Group, levels=c("Group Long",
                                        "Group Short",
                                        "Group None")),
         Response = ifelse(Response == 1, "Target", "Alternative"),
         Response = ifelse(Responding > 22.5, "Control", Response),
         Response = ifelse(Responding < -22.5, "Control", Response)) %>%
  select(Group, Response, Responding) %>%
  filter(Response != "Control")

modDatabase.lev %>%
  group_by(Group) %>%
  dplyr::summarise(
    Ave = mean(Responding),
    sd  = sd(Responding)
  ) %>%
  kable(caption = "Reference Swipe [Unscreened]") %>%
  kableExtra::kable_styling(full_width = TRUE)

car::leveneTest(Responding ~ Group, data = modDatabase.lev) %>%
  tidy() %>% 
  kable(caption = "Levenes Test [Unscreened]") %>%
  kableExtra::kable_styling(full_width = TRUE)

```

